Turbulence and Particle Acceleration in Giant Radio Haloes: the Origin of Seed Electrons

### 2016-06-20 paper.tex
unified notation for _p and _CR subscripts

\renewcommand{\vec}{\ensuremath{\mathbfit}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Vph}{\varv_\mathrm{ph}}
\newcommand{\mug}{\umu G}
\newcommand{\RH}{R_\rmn{RH}}
\newcommand{\bvel}{\ensuremath{\boldsymbol{\varv}}}
\newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
\newcommand\eb{\epsilon_\rmn{B}}
\newcommand{\dps}{\displaystyle}
\newcommand{\p}{\rmn{p}}
\newcommand{\kB}{k_{\rmn{B}}}
\newcommand{\eps}{\varepsilon}

@@

We use a simple test-particle model for the CR acceleration and
injection, where each shock injects CRs that trace a power-law in
momentum,
\begin{equation}
  f_\p(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
  \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
        {(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}
\end{equation}
determined by the normalisation $C(t)$ and the spectral index
$\alpha_{\rmn{inj}}$ that depends on the adiabatic index
$\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
$\mathcal{M}$. It is given by the ratio of the upstream velocity
($\varv_2$) and the sound speed ($c_{\rm s}$). The CR number density and CR
energy density are derived from
\begin{eqnarray}
n_\rmn{p} &=&
\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p)\\
\eps_\rmn{p} &=&
\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p) \,E(p),
\end{eqnarray}
where $E(p) = (\sqrt{1+p^2} -1)\, m_{\rmn{p}}\,c^2$ is the kinetic energy of a
proton with momentum $p$. We adopt a fit to Monte Carlo simulations of the
thermal leakage process that relates the momentum of injected protons
($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the shocked plasma
\citep{kang11}:
\begin{eqnarray}
  \label{eq:qinj}
  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} =
  x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m_{\rmn{p}} c^2}}\,, \nonumber \\
  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{\varv_2}{p_{\rmn{th}}\,c} \left(1+
  \frac{1.07}{\eb}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
\end{eqnarray}
Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
shock normal. The physical range of $\eb$ is quite uncertain due to
complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
which -- as we will later see -- corresponds to a conservative maximum
energy acceleration efficiency for protons of $0.1$. To derive the
acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
particle injection efficiency, which is the fraction of downstream
thermal gas particles which experience diffusive shock acceleration
\citep[for details see][]{pinzke13},
\begin{equation}
  \label{eq:eta}
  \eta_\rmn{p,lin} =
  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
  \rmn{e}^{-x_\rmn{inj}^2}.
\end{equation}
The particle injection efficiency is a strong function of
$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
energy density of CRs that are injected and accelerated at the shock
(neglecting the CR back reaction on the shock) is given by
\begin{equation}
\label{eq:CR_energy} 
  \Delta\eps_\rmn{p,lin} =
  \eta_\rmn{p,lin}(\mathcal{M})\,n_\rmn{th}(T_2)
  \,\frac{\eps_\p}{n_\p}
\end{equation}
and the CR energy injection and acceleration efficiency is:
\begin{equation}
  \zeta_\rmn{lin} =
  \frac{\Delta\eps_\rmn{p,lin}}{\Delta\eps_\rmn{diss}},
   \quad\mbox{where}\quad
  \Delta\eps_\rmn{diss} = \eps_\rmn{th2} - \eps_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
\label{eqn:energy_frac}  
\end{equation}
The dissipated energy density in the downstream regime,
$\Delta\eps_\rmn{diss}$, is given by the difference of the thermal
energy densities in the pre- and post-shock regimes, corrected for the
adiabatic energy increase due to gas compression.

We limit the acceleration efficiency to $\zeta_\rmn{max}$ by
steepening the spectral index of the injected population
$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_\rmn{lin}
\leq \zeta_\rmn{max}$ is always fulfilled. The slope
$\alpha_\rmn{inj}$ impact $\zeta_\rmn{inj}$ via the mean energy per
particle, $\eps_\rmn{p}/n_\rmn{p}$. This
procedure conserves energy and is motivated by models of non-linear
shock acceleration where a sub-shock with a lower compression ratio
(and hence steeper spectral index) forms
\citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
find that for strong shocks where $\alpha \lesssim 2.3$ the spectral
slope is steepened by a maximum of $\sim 10$ per cent in low
temperature regimes ($\kB T\sim 0.1$~keV), while the steepening is much
smaller for high temperature regimes ($\kB T\sim 10$~keV) that are more
relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
CR number density $n_\rmn{p}$. Hence we can solve for the
renormalised normalisation constant $C_\rmn{sub}$ using $n_\rmn{p}$
and Eqn.~\ref{eq:eta}:
\begin{equation}
  \label{eq:Cp_sub}
  C_\rmn{sub}=\eta_\rmn{p,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
\end{equation}
where the new distribution function is given by $f_\p(p,t)= C_\rmn{sub}
p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
accelerated proton-to-dissipated energy in the downstream of strong
shocks that varies from $\zeta_\rmn{max} \sim 0.01-0.1$, depending on
the adopted model (for more details, see Section \ref{sec:results}).

@@

The bulk of the CRps are injected by relatively low Mach number shocks
and parametrized by $f_\rmn{p,inj}(p) =
C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where $\alpha_\rmn{inj}\approx
2.5$ in our simulations. The CRps approximately trace the thermal gas
with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
\citep{pinzke10,2016MNRAS.459...70V}, where the normalisation is fixed
by the injected CR energy in the last 650~Myrs. Our simulations show
that it approximately amounts to 0.03 per cent of the thermal energy inside
the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{p,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalisation by requiring $\int_0^{R_{200}}\eps_\rmn{p,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.003$. Note
that the injected energy in the last 650 Myr is smaller by about a factor of 10
in comparison to the cumulative CR energy injected over the entire cosmological
history of the cluster, but this component is nonetheless important since above
1 GHz the radio emission is dominated by CRes injected during the merger, which
have not yet had time to cool.  Similarly, the initial CRe distribution is given
by the steady state between cooling (Coulomb, inverse Compton, and synchrotron)
and injection of secondary CRes from $f_\rmn{p,0}$.  The diffusion constant
$D_{pp} \propto X_{\rm tu}^{2} \eps_{\rm th}^{\alpha-1} \sqrt{T} k_L$ is
calculated for each radial bin. All parameters and assumptions are similar to
what is used for our simulated cluster (see Sect.~\ref{sec:results}). Our
fiducial model assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm
  CR, spat}=1.0$, and $k_L=2 \upi/\lambda_L$ where $\lambda_L=100$ kpc. We also
assume a fixed acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.

@@

We have seen that the radio luminosity depends very sensitively on $\tau_{\rm
  cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Fig
\ref{fig:param_comp}; note from equation \ref{eq:Dpp_scaling} that $\tau_{\rm D}
\propto X_{\rm tu}^{-2}$). Since this raises questions of fine-tuning in $X_{\rm
  tu}$ to explain the observations, it is worth understanding this property in
more detail. To this end, we ignore cooling which is a good approximation for
the CR protons, because hadronic cooling times are long in comparison to the
other relevant timescales of the problem.\footnote{In principle, CRp can still
  lose energy via wave heating, at a rate $\bmath{\varv_{\rm A} \cdot \nabla} P_{c}$,
  but we assume CR streaming is suppressed during mergers, when they are
  spatially confined by scattering.} In this case, $\dot{p}= p/\tau_{\rm D}$,
and after a time $\tau_{\rm cl}$, we have $p \rightarrow p \, {\rm
  exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the fact that $\tau_{\rm
  D}$ is momentum independent). For an initial power law distribution function
$f(p) = C p^{-\alpha}$, this momentum increase can be rewritten as a change of
normalisation, $f(p) = \tilde{C} p^{-\alpha}$, where $\tilde{C} = {\rm exp}(
\alpha \tau_{\rm cl}/\tau_{\rm D})$. A slightly more careful derivation by
direct solution of the Fokker-Planck equation yields:
\begin{equation}
  \dot{f} = {{\partial }\over{\partial p}}
  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
\end{equation}
with the analytic solution given by
\begin{equation}
  \label{eq:Creacc}
  \tilde{C}= 
  C \exp{\left[\frac{(2+\alpha)(\alpha-1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,.
\end{equation}
This exponential sensitivity to $\tau_{\rm cl}/\tau_{\rm D}$ lies behind the extreme sensitivity to $X_{\rm tu}$ in Fig \ref{fig:param_comp}.

@@

An obvious candidate for $\tau_{\rm decay}$ is: 
\begin{equation}
\tau_{\rm edd} = \frac{L}{\varv_{\rm c}}
\end{equation}
i.e., the eddy turnover time at the outer scale. This is subject to
uncertainties about the location of the outer scale $L$; estimates in the
literature range from $L \sim 0.1-1$ Mpc. It is also worth remembering that MHD
turbulence only applies for $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n
scale where $\varv \sim \varv_{\rm A}$. Invoking fast modes, Kraichnan scalings,
etc., is only valid below these scales. For $l > l_{\rm A}$, turbulence is
basically hydrodynamic and Kolmogorov in nature. The momentum diffusion
coefficient can thus be split up into two components:
\begin{equation}
D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm c} < l < l_{\rm A}]
\end{equation}
From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm c} < l < l_{\rm A}$, we get: 
\begin{equation}
\frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}} = \frac{k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}} = A^{-1/2} \beta = 0.5 \left( \frac{\beta}{50} \right) 
\end{equation}
where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov scalings, and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation \ref{eqn:k_c}).  Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $\mathcal{M}_{\rm A}^{1/2}$). 
Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $\varv_{\rm A}$. The turbulent reacceleration time is: 
\begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
\label{eqn:tau_D} 
\end{equation}
where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation \ref{eqn:k_c}. The turbulent decay time is given by the cascade time of fast modes (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}): 
\begin{equation}
\tau_{\rm decay} = \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}^{}}\,.
\label{eqn:tau_decay} 
\end{equation} 
This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
\begin{equation}
\tau_{\rm decay} =\frac{L}{\varv_{\rm c}} \left(\frac{c_{\rm s}}{\varv_{\rm c}} \right)^{2} \frac{\varv_{\rm A}}{c_{\rm s}} = 0.7 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{100} \right)^{-1/2}
\end{equation}
where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. Thus $\tau_{\rm decay} \sim \tau_{\rm edd}$, but we prefer to use the expression for $\tau_{\rm edd}$, since it is more physically correct and leads to more revealing scalings.

>>>>

\renewcommand{\vec}{\ensuremath{\mathbfit}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Vph}{\varv_\mathrm{ph}}
\newcommand{\mug}{\umu G}
\newcommand{\RH}{R_\rmn{RH}}
\newcommand{\bvel}{\ensuremath{\boldsymbol{\varv}}}
\newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
\newcommand{\eb}{\epsilon_B}
\newcommand{\dps}{\displaystyle}
\newcommand{\p}{\rmn{p}}
\newcommand{\kB}{k_{\rmn{B}}}
\newcommand{\eps}{\varepsilon}
\newcommand{\CR}{\rmn{CR}}

@@

We use a simple test-particle model for the CR acceleration and
injection, where each shock injects CRs that trace a power-law in
momentum,
\begin{equation}
  f_\p(p,t) = C(t)\,p^{\alpha_\rmn{inj}}\,,\quad
  \alpha_\rmn{inj}=\frac{(\gamma_\rmn{ad}+1)\mathcal{M}^2}
        {(\gamma_\rmn{ad}-1)\mathcal{M}^2+2}
\end{equation}
determined by the normalisation $C(t)$ and the spectral index
$\alpha_{\rmn{inj}}$ that depends on the adiabatic index
$\gamma_\rmn{ad} = 5/3$ and the Mach number of the shock
$\mathcal{M}$. It is given by the ratio of the upstream velocity
($\varv_2$) and the sound speed ($c_{\rm s}$). The CR number density and CR
energy density are derived from
\begin{eqnarray}
n_\CR &=&
\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p)\\
\eps_\CR &=&
\int_{p_\rmn{inj}}^\infty \dd p\, f_\p(p) \,E(p),
\end{eqnarray}
where $E(p) = (\sqrt{1+p^2} -1)\, m_{\rmn{p}}\,c^2$ is the kinetic energy of a
proton with momentum $p$. We adopt a fit to Monte Carlo simulations of the
thermal leakage process that relates the momentum of injected protons
($p_\rmn{inj}$) to the thermal energy ($p_\rmn{th}$) of the shocked plasma
\citep{kang11}:
\begin{eqnarray}
  \label{eq:qinj}
  p_\rmn{inj} &=& x_\rmn{inj} p_\rmn{th} =
  x_\rmn{inj} \sqrt{\frac{2 \,\kB T_2}{m_{\rmn{p}} c^2}}\,, \nonumber \\
  \rmn{where}\quad x_\rmn{inj} &\approx& 1.17 \frac{\varv_2}{p_{\rmn{th}}\,c} \left(1+
  \frac{1.07}{\eb}\right) \left(\frac{\mathcal{M}}{3}\right)^{0.1}\,.
\end{eqnarray}
Here $\eb = B_0/B_{\perp}$, $B_0$ is the amplitude of the downstream
MHD wave turbulence, and $B_{\perp}$ is the magnetic field along the
shock normal. The physical range of $\eb$ is quite uncertain due to
complex plasma interactions. In this paper, we adopt $\eb = 0.23$,
which -- as we will later see -- corresponds to a conservative maximum
energy acceleration efficiency for protons of $0.1$. To derive the
acceleration efficiency, $\zeta_\rmn{inj}$, we first have to infer the
particle injection efficiency, which is the fraction of downstream
thermal gas particles which experience diffusive shock acceleration
\citep[for details see][]{pinzke13},
\begin{equation}
  \label{eq:eta}
  \eta_\rmn{p,lin} =
  \frac{4}{\sqrt{\upi}}\,\frac{x_\rmn{inj}^3}{\alpha_\rmn{inj}-1}\,
  \rmn{e}^{-x_\rmn{inj}^2}.
\end{equation}
The particle injection efficiency is a strong function of
$x_\rmn{inj}$ that depends on both $\mathcal{M}$ and $\eb$. The
energy density of CRs that are injected and accelerated at the shock
(neglecting the CR back reaction on the shock) is given by
\begin{equation}
\label{eq:CR_energy} 
  \Delta\eps_\rmn{CR,lin} =
  \eta_\rmn{p,lin}(\mathcal{M})\,n_\rmn{th}(T_2)
  \,\frac{\eps_\CR}{n_\CR}
\end{equation}
and the CR energy injection and acceleration efficiency is:
\begin{equation}
  \zeta_\rmn{lin} =
  \frac{\Delta\eps_\rmn{p,lin}}{\Delta\eps_\rmn{diss}},
   \quad\mbox{where}\quad
  \Delta\eps_\rmn{diss} = \eps_\rmn{th2} - \eps_\rmn{th0}\,\left(\frac{\rho_2}{\rho_0}\right)^{\gamma_\rmn{ad}}\,.
\label{eqn:energy_frac}  
\end{equation}
The dissipated energy density in the downstream regime,
$\Delta\eps_\rmn{diss}$, is given by the difference of the thermal
energy densities in the pre- and post-shock regimes, corrected for the
adiabatic energy increase due to gas compression.

We limit the acceleration efficiency to $\zeta_\rmn{max}$ by
steepening the spectral index of the injected population
$\alpha_\rmn{inj}$ to $\alpha_\rmn{sub}$ so that $\zeta_\rmn{lin}
\leq \zeta_\rmn{max}$ is always fulfilled. The slope
$\alpha_\rmn{inj}$ impact $\zeta_\rmn{inj}$ via the mean energy per
particle, $\eps_\rmn{p}/n_\rmn{p}$. This
procedure conserves energy and is motivated by models of non-linear
shock acceleration where a sub-shock with a lower compression ratio
(and hence steeper spectral index) forms
\citep[e.g.,][]{2000ApJ...540..292E}. Given our assumed $\eb=0.23$, we
find that for strong shocks where $\alpha \lesssim 2.3$ the spectral
slope is steepened by a maximum of $\sim 10$ per cent in low
temperature regimes ($\kB T\sim 0.1$~keV), while the steepening is much
smaller for high temperature regimes ($\kB T\sim 10$~keV) that are more
relevant for clusters. Since $p_\rmn{inj}$ remains fixed, so does the
CR number density $n_\CR$. Hence we can solve for the
renormalised normalisation constant $C_\rmn{sub}$ using $n_\CR$
and Eqn.~\ref{eq:eta}:
\begin{equation}
  \label{eq:Cp_sub}
  C_\rmn{sub}=\eta_\rmn{p,lin}\,(\alpha_\rmn{sub}-1)\,p_\rmn{inj}^{\alpha_\rmn{sub}-1}\,,
\end{equation}
where the new distribution function is given by $f_\p(p,t)= C_\rmn{sub}
p^{-\alpha_\rmn{sub}}$. We set an upper limit on the ratio of
accelerated proton-to-dissipated energy in the downstream of strong
shocks that varies from $\zeta_\rmn{max} \sim 0.01-0.1$, depending on
the adopted model (for more details, see Section \ref{sec:results}).

@@

The bulk of the CRps are injected by relatively low Mach number shocks
and parametrized by $f_\rmn{p,inj}(p) =
C_\rmn{inj}\,p^{-\alpha_\rmn{inj}}$, where $\alpha_\rmn{inj}\approx
2.5$ in our simulations. The CRps approximately trace the thermal gas
with $C_\rmn{inj} \propto \eps_\rmn{th}^{\alpha_\rmn{CR,spat}}$
\citep{pinzke10,2016MNRAS.459...70V}, where the normalisation is fixed
by the injected CR energy in the last 650~Myrs. Our simulations show
that it approximately amounts to 0.03 per cent of the thermal energy inside
the virial radius, i.e.  $\int_0^{R_{200}}\eps_\rmn{CR,inj} \rmn{d}
V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} =
0.0003$. The spectrum of the initial CRp distribution is determined by
the steady state between injection and cooling,
\begin{equation}
 f_\rmn{p,0} \propto \frac{\int_p^\infty f_\rmn{p,inj}(p') 
\rmn{d}p'}{\displaystyle\left|{{\rmn{d}p}\over{\rmn{d}t}}\right|_{\rm Coul}+\frac{p}{\tau_{\rm had}}}\,,
\end{equation}
where we fix the normalisation by requiring $\int_0^{R_{200}}\eps_\rmn{CR,0}
\rmn{d}V\left(\int_0^{R_{200}}\eps_\rmn{th} \rmn{d}V\right)^{-1} = 0.003$. Note
that the injected energy in the last 650 Myr is smaller by about a factor of 10
in comparison to the cumulative CR energy injected over the entire cosmological
history of the cluster, but this component is nonetheless important since above
1 GHz the radio emission is dominated by CRes injected during the merger, which
have not yet had time to cool.  Similarly, the initial CRe distribution is given
by the steady state between cooling (Coulomb, inverse Compton, and synchrotron)
and injection of secondary CRes from $f_\rmn{p,0}$.  The diffusion constant
$D_{pp} \propto X_{\rm tu}^{2} \eps_{\rm th}^{\alpha-1} \sqrt{T} k_L$ is
calculated for each radial bin. All parameters and assumptions are similar to
what is used for our simulated cluster (see Sect.~\ref{sec:results}). Our
fiducial model assumes $X_{\rm tu} = 0.2$, $\alpha_{\rm tu} =0.8$, $\alpha_{\rm
  CR, spat}=1.0$, and $k_L=2 \upi/\lambda_L$ where $\lambda_L=100$ kpc. We also
assume a fixed acceleration time of $\tau_{\rm cl} = 650 \, {\rm Myr}$.

@@

We have seen that the radio luminosity depends very sensitively on $\tau_{\rm
  cl}/\tau_{\rm D}$, through the very sensitive dependence on $X_{\rm tu}$ (Fig
\ref{fig:param_comp}; note from equation \ref{eq:Dpp_scaling} that $\tau_{\rm D}
\propto X_{\rm tu}^{-2}$). Since this raises questions of fine-tuning in $X_{\rm
  tu}$ to explain the observations, it is worth understanding this property in
more detail. To this end, we ignore cooling which is a good approximation for
the CR protons, because hadronic cooling times are long in comparison to the
other relevant timescales of the problem.\footnote{In principle, CRp can still
  lose energy via wave heating, at a rate $\bmath{\varv_{\rm A} \cdot \nabla} P_\CR$,
  but we assume CR streaming is suppressed during mergers, when they are
  spatially confined by scattering.} In this case, $\dot{p}= p/\tau_{\rm D}$,
and after a time $\tau_{\rm cl}$, we have $p \rightarrow p \, {\rm
  exp}(\tau_{\rm cl}/\tau_{\rm D})$ (where we have used the fact that $\tau_{\rm
  D}$ is momentum independent). For an initial power law distribution function
$f(p) = C p^{-\alpha}$, this momentum increase can be rewritten as a change of
normalisation, $f(p) = \tilde{C} p^{-\alpha}$, where $\tilde{C} = {\rm exp}(
\alpha \tau_{\rm cl}/\tau_{\rm D})$. A slightly more careful derivation by
direct solution of the Fokker-Planck equation yields:
\begin{equation}
  \dot{f} = {{\partial }\over{\partial p}}
  p^2 D_{pp} {{\partial }\over{\partial p}} \frac{f}{p^2}\,,
\end{equation}
with the analytic solution given by
\begin{equation}
  \label{eq:Creacc}
  \tilde{C}= 
  C \exp{\left[\frac{(2+\alpha)(\alpha-1)}{4}\frac{\tau_\rmn{cl}}{\tau_\rmn{D}}\right]}\,.
\end{equation}
This exponential sensitivity to $\tau_{\rm cl}/\tau_{\rm D}$ lies behind the extreme sensitivity to $X_{\rm tu}$ in Fig \ref{fig:param_comp}.

@@

An obvious candidate for $\tau_{\rm decay}$ is: 
\begin{equation}
\tau_{\rm edd} = \frac{L}{\varv_{\rm c}}
\end{equation}
i.e., the eddy turnover time at the outer scale. This is subject to
uncertainties about the location of the outer scale $L$; estimates in the
literature range from $L \sim 0.1-1$ Mpc. It is also worth remembering that MHD
turbulence only applies for $l < l_{\rm A}$, where $l_{\rm A}$ is the Alfv{\'e}n
scale where $\varv \sim \varv_{\rm A}$. Invoking fast modes, Kraichnan scalings,
etc., is only valid below these scales. For $l > l_{\rm A}$, turbulence is
basically hydrodynamic and Kolmogorov in nature. The momentum diffusion
coefficient can thus be split up into two components:
\begin{equation}
D_{pp} = D_{pp}^{\rm HD}[l_{\rm A} < l < L] + D_{pp}^{\rm MHD}[l_{\rm cut} < l < l_{\rm A}]
\end{equation}
From equations (\ref{eqn:diffusion}) and (\ref{eqn:k_W}), and assuming Kolmogorov turbulence from $l_{\rm A} < l < L$ and Kraichnan turbulence from $l_{\rm cut} < l < l_{\rm A}$, we get: 
\begin{equation}
\frac{D_{pp}^{\rm HD}}{D_{pp}^{\rm MHD}} = \frac{k_L^{2/3}k_{\rm A}^{1/3} \varv_{\rm c}^{2}}{k_{\rm A}^{1/2}k_{\rm cut}^{1/2} \varv_{\rm A}^{2}} = A^{-1/2} \beta = 0.5 \left( \frac{\beta}{50} \right) 
\end{equation}
where we have used $k_{\rm A} = k_L \mathcal{M}_{\rm A}^{3}$ (from Kolmogorov scalings, and $\mathcal{M}_{\rm A} = \varv_{\rm c}/\varv_{\rm A}$ is the Alfv{\'e}n Mach number of the turbulence, $\beta \approx c_{\rm s}^{2}/\varv_{\rm A}^{2}$, and the cutoff scale $k_{\rm cut}$ (equation \ref{eqn:k_c}).  Thus, the contribution of the two regimes are comparable (as we shall see later, this is not true if one incorrectly assumes Kraichnan scalings apply from the outer scale $L$; this boosts the contribution of the scales where $l_{\rm A} < l < L$ by a factor $\mathcal{M}_{\rm A}^{1/2}$). 
Henceforth, we can consider the outer scale of the fast modes to be $l_{\rm A}$, with velocity $\varv_{\rm A}$. The turbulent reacceleration time is: 
\begin{equation}
\tau_{\rm D} = \frac{p^{2}}{4 D_{pp}} = C_{\rm D} A^{1/2} c k_{\rm A} \frac{\varv_{\rm A}^{2}}{c_{\rm S}^{2}}
\label{eqn:tau_D} 
\end{equation}
where $C_{\rm D} = 2/(5 \upi)$, $A\approx 11000$, and we have used equation \ref{eqn:k_c}. The turbulent decay time is given by the cascade time of fast modes (\citealt{2004ApJ...614..757Y}; see equation \ref{eqn:cascade}): 
\begin{equation}
\tau_{\rm decay} = \frac{c_{\rm s}}{\varv_{\rm A}^{2} k_{\rm A}^{}}\,.
\label{eqn:tau_decay} 
\end{equation} 
This can be related to the eddy turnover time at the outer scale $\tau_{\rm edd}$ from $l_{\rm A} = L \mathcal{M}_{\rm A}^{-3}$ to: 
\begin{equation}
\tau_{\rm decay} =\frac{L}{\varv_{\rm c}} \left(\frac{c_{\rm s}}{\varv_{\rm c}} \right)^{2} \frac{\varv_{\rm A}}{c_{\rm s}} = 0.7 \, \tau_{\rm edd} \left(\frac{\tilde{X}_{\rm tu}}{0.2}\right)^{-1}  \left(\frac{\beta}{100} \right)^{-1/2}
\end{equation}
where we have used $\tilde{X}_{\rm tu} \approx (\varv_{\rm c}/c_{\rm s})^{2}$ and $c_{\rm s}/\varv_{\rm A} = \beta^{1/2}$. Thus $\tau_{\rm decay} \sim \tau_{\rm edd}$, but we prefer to use the expression for $\tau_{\rm edd}$, since it is more physically correct and leads to more revealing scalings.
